Refining character relationships using embeddings of textual units : a case study on Les Misérables

### 2022-10-03 article/paper1.tex
create timeline with CA

>>>>

\subsubsection{WV unit embeddings}

% ----------------------------------------------

\begin{table*}[!bh]
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		T1 & T2 & T3 & T4 & T5 \\ \hline
		huissier (1.4) & cuirassier (3.38) & gamin (1.92) & émeute (1.48) & sable (3.04) \\ \hline
		hôte (1.11) & infanterie (2.9) & mine (1.38) & révolte (0.86) & berge (2.32) \\ \hline
		arras (0.92) & sacrement (2.69) & farce (0.81) & bourgeoisie (0.84) & égout (2.16) \\ \hline
		lampe (0.91) & brigade (2.41) & ignorance (0.74) & populaire (0.82) & voûte (1.9) \\ \hline
		montreuil (0.81) & division (2.4) & jondrette (0.7) & insurrection (0.81) & vase (1.89) \\ 
		\hline
	\end{tabular}

	\begin{tabular}{|c|c|c|c|c|}
		\hline
		Cosette-Valjean\_1 & Cosette-Valjean\_2 & Cosette-Valjean\_3 & Cosette-Valjean\_4 & Cosette-Valjean\_5 \\ \hline
		maladie (0.49) & façade (0.68) & - & promenade (0.5) & noce (1.27) \\ \hline
		médecin (0.48) & corbillard (0.66) & - &chaîne (0.47) & marié (0.93) \\ \hline
		demain (0.33) & mestienne (0.6) & - & blessure (0.46) & mardi (0.89) \\ \hline
		surprise (0.28) & bâtiment (0.56) & - &tuyau (0.45) & mariage (0.86) \\ \hline
		auprès (0.28) & cul (0.55) & - &luxembourg (0.44) & file (0.65) \\ \hline
	\end{tabular}

	\label{CA_TIME_REG_word_vs_obj}
	\caption{The 5 most associated words (similarity in parentheses) vs volumes objects (top) and Cosette-Valjean relationship as found in each tome, regarding the \textbf{CA-REG} method ($\lambda = 0.01$). Note that no co-occurrence between Cosette and Valjean were automatically found in volume 3.}
\end{table*}
